A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-18 writeup/paper.tex
new map
Editing related work

%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=7in]{figures/turkermap}
\caption{}
\label{map}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Background and Related Work}
%\section{Mechanical Turk}
Amazon's Mechanical Turk (MTurk) is an online crowdsourcing marketplace which gives employers and researchers access to a large, low-cost, human workforce. MTurk advertises `artificial artificial intelligence'; it provides a simple interface for accessing human skill, allowing small tasks, which are too difficult for computers, to be completed with the speed and scale of an automated process. When Amazon first introduced MTurk, payment was offered only in Amazon credits. As the service grew, payment switched to US dollars, and more recently has expanded to include foreign currencies, such as the rupee. Currently, MTurk claims over half a million workers from 190 countries, making it a compelling source of data for diverse natural language applications.

Within MTurk, those who need work completed (`requesters') post individual `Human Intelligence Tasks,' or just `HITs'. A typical HIT  requires a few minutes of work and pays a few cents, although there is significant variation across HITs. Once a HIT is posted, MTurk workers (`Turkers') are free to choose to complete the HITs which interest them. Worker identities remain anonymous to requesters, and all payment occurs through Amazon. Requesters are able to accept submitted work or reject work that they do not feel meets their standards, and only pay workers from whom they accepted tasks.

The convenience and low cost of using MTurk has made it popular among researchers. Because of the lack of oversight and the high potential for spam, however, most of the data collected from MTurk has been limited to simple tasks for which inter-annotator agreement is expected to be high (see Related Work section below). We explore the idea that MTurk's machinery is flexible enough to support more complex tasks requiring more nuanced quality control mechanisms, which could allow it to be a competitive alternative to professional data annotations.

\section{Related Work}
Crowdsourced data has been used in a variety of machine learning applications, including computer vision (Sorokin et al.), paraphrasing (Nakov et al.) and sentiment analysis \cite{Snow2008}. More recently, in 2010, NAACL hosted a workshop on Creating Speech and Language Data with MTurk, in which MTurk was used to generate data for 24 different natural language tasks \cite{callisonburch-dredze:2010:MTURK}.

>>>>

%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=7in]{figures/turkermap-color}
\caption{}
\label{map}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Background and Related Work}
%\section{Background on Mechanical Turk and Related Work}
%\section{Mechanical Turk}
Amazon's Mechanical Turk (MTurk) is an online marketplace for work which gives employers and researchers access to a large, low-cost, human workforce. MTurk provides a simple interface for accessing human skill, allowing requesters to provide micro-payments in return for workers completing micro-tasks.  The basic units of work on MTurk are called ``Human Intelligence Tasks'' (HITs), which suggests that it was designed to accommodate tasks that are difficult for computers, but simple for people. This allows for research into human computation, where people can be treated as a function call \cite{vonAhn2008,Little2009,quinn-bederson:2011}, as well as for large-scale annotation of training data for machine learning applications, including computer vision \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10} and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK}. 
%In 2010, NAACL hosted a workshop on Creating Speech and Language Data with MTurk, in which MTurk was used to generate data for 24 different natural language tasks \cite{callisonburch-dredze:2010:MTURK}.

Several reports examine Mechanical Turk as a marketplace \cite{ipeirotis:2010:marketplace,lehdonvirta-ernkvist:2011}.  When Amazon introduced MTurk, it first offered payment only in Amazon credits, and later offered direct payment in US dollars. More recently has expanded to include one foreign currency, the Indian rupee. Despite its payments being limited to two currencies or Amazon credits, MTurk claims over half a million workers from 190 countries.\footnote{https://requester.mturk.com/tour}  This suggest that it has a diverse worker population that should represent a wide variety of languages.

%Within MTurk, those who need work completed (`requesters') post individual HITs. A typical HIT  requires a few minutes of work and pays a few cents, although there is significant variation across HITs. Once a HIT is posted, MTurk workers (`Turkers') are free to choose to complete the HITs which interest them. Worker identities remain anonymous to requesters, and all payment occurs through Amazon. Requesters are able to accept submitted work or reject work that they do not feel meets their standards, and only pay workers from whom they accepted tasks.

%The convenience and low cost of using MTurk has made it popular among researchers. Because of the lack of oversight and the high potential for spam, however, most of the data collected from MTurk has been limited to simple tasks for which inter-annotator agreement is expected to be high (see Related Work section below). We explore the idea that MTurk's machinery is flexible enough to support more complex tasks requiring more nuanced quality control mechanisms, which could allow it to be a competitive alternative to professional data annotations.

%\section{Related Work}
